Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-09 paper/agree.tex
Format and mark text that needs to change

The goal of this section is to illustrate in more detail the process a
system designer follows to add cyber requirements to the AGREE
specifications and then automatically transform the system to insert
the high-assurance components. The AGREE specifications generated by
the transforms for the high-assurance components are also
explained. The section ends with a concise formal statement of the
meaning of an AGREE specification for a high-assurance component. This
meaning is what must be preserved by the synthesis.

@@

The \emph{Alert if start is not bounded relative to a request}
guarantee is an invariant on the expression \texttt{policy or since},
meaning that either the policy holds or the alert is
sounding. The \texttt{policy} is defined by two local
values: \texttt{current} and \texttt{previous}. The \texttt{current}
value is asserted when in the current time step there is a request
with a response, or there is no request and no response.

@@

As noted previously, the original system fails to guarantee the cyber requirements. BriefCASE provides two transformations to address the failing requirements: inserting a filter and inserting a monitor. The component is added by selecting the connection in the model where the high-assurance component is to be added, and then choosing the appropriate transformation. The system designer can provide transform configuration parameters in a wizard, as shown in \figref{fig:dialogue}. The policy of the high-assurance component can be stated directly in the wizard, or it can be left  blank. In this example, the policy is specified as \texttt{WELL\_FORMED\_AUTOMATION\_RESPONSE(Input)}.
Additionally, because a transformation is ultimately driven by a cyber requirement, BriefCASE updates an embedded Resolute assurance case~\cite{resolute-destion}.  Resolute keeps track of the evidential artifacts necessary for supporting the requirement, and can be run at any time to determine whether those artifacts are valid.
%Additionally, the filter can be attached to any requirement the vulnerability analysis. This association is useful the the assurance case from the Resolute tool [CITE DESTION 2021]. The \emph{OK} button creates the component and inserts it accordingly into the implementation

The AGREE contract specification generated by the transform is shown in \figref{fig:assurance}(a). The guarantee is stylized for synthesis and completely defines the meaning of the output under every possible input.
%A similar dialogue exist for inserting monitors that allows the system designer to add and remove inputs as needed.
The resulting AGREE specification for the monitor in this example is shown in \figref{fig:assurance}(b). The \texttt{is\_latched} value makes the alert persistent, meaning that once the alert is raised, it is always raised.  This behavior is one of the several options available in the dialogue. The definition for \texttt{policy} is taken by the system developer from the contract in \figref{fig:sw}. As before, the guarantees for the outputs are autogenerated by the tool and completely define each output under every possible input.

>>>>

The goal of this section is to illustrate in more detail the process a system designer follows to add cyber requirements to the AGREE specifications and then automatically transform the system to insert the high-assurance components.
The AGREE specifications generated by the transforms for the high-assurance components are also explained.

@@

REPLACE ALL: 
The \emph{Alert if start is not bounded relative to a request} guarantee is an invariant on the expression \texttt{policy or since}, meaning that either the policy holds or the alert is sounding.
The \texttt{policy} is defined by two local values: \texttt{current} and \texttt{previous}.
The \texttt{current} value is asserted when in the current time step there is a request with a response, or there is no request and no response.

@@

As noted previously, the original system fails to guarantee the cyber requirements.
BriefCASE provides two transformations to address the failing requirements: inserting a filter and inserting a monitor.
The component is added by selecting the connection in the model where the high-assurance component is to be added, and then choosing the appropriate transformation.
The system designer can provide transform configuration parameters in a wizard, as shown in \figref{fig:dialogue}.
The policy of the high-assurance component can be stated directly in the wizard, or it can be left blank.
In this example, the policy is specified as \texttt{WELL\_FORMED\_AUTOMATION\_RESPONSE(Input)}.
Additionally, because a transformation is ultimately driven by a cyber requirement, BriefCASE updates an embedded Resolute assurance case~\cite{resolute-destion}.
REMOVE: Resolute keeps track of the evidential artifacts necessary for supporting the requirement, and can be run at any time to determine whether those artifacts are valid.

The AGREE contract specification generated by the transform is shown in \figref{fig:assurance}(a).
The guarantee is stylized for synthesis and completely defines the meaning of the output under every possible input.
The resulting AGREE specification for the monitor in this example is shown in \figref{fig:assurance}(b).
The \texttt{is\_latched} value makes the alert persistent, meaning that once the alert is raised, it is always raised.
This behavior is one of the several options available in the dialogue.
The definition for \texttt{policy} is taken by the system developer from the contract in \figref{fig:sw}.
As before, the guarantees for the outputs are autogenerated by the tool and completely define each output under every possible input.
